Reproducible Summary Tables with gtsummary

### 2020-12-09 RJtemplate_gtsummary_submission.tex

\section{Section title in sentence case}

Introductory section which may include references in parentheses
\citep{R}, or cite a reference such as \citet{R} in the text.

\section{Another section}

This section may contain a figure such as Figure~\ref{figure:rlogo}.

\begin{figure}[htbp]
  \centering
  \includegraphics{Rlogo-5}
  \caption{The logo of R.}
  \label{figure:rlogo}
\end{figure}

\section{Another section}

There will likely be several sections, perhaps including code snippets, such as:

\begin{example}
  x <- 1:10
  result <- myFunction(x)
\end{example}

\section{Summary}

This file is only a basic article template. For full details of \emph{The R Journal} style and information on how to prepare your article for submission, see the \href{https://journal.r-project.org/share/author-guide.pdf}{Instructions for Authors}.

>>>>

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{data-summaries}{%
\section{Data Summaries}\label{data-summaries}}

% adding table describing trial dataset
\input{tbl_trial_desc.tex}
